30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-14 paper.tex
Fixed conflict structure problem

	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@

@@

			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file. Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces. This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file. The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.

			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his direct neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more. Results of queries are being cached in intermediate nodes to reduce the time for a query response. To prevent looping of the requests, each request contains a random identifier. The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.

>>>>

@@

		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file. Another key is the Signed-Subspace key (SSK) which enables personal namespaces. This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file. The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.

		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more. Results of queries are being cached in intermediate nodes to reduce the time for a query response. To prevent looping of the requests, each request contains a random identifier. The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.

@@

		MIX networks are typically high latency networks and traffic in it moves slow. Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order. Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead. MorphMix has been developed as a low latency and high performance network. As such, it will not hold messages for very long, nor will it use cover traffic.

		In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism. Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefore control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel. Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.

		An important part of MorphMix is the ability to detect malicious tunnels. Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly. Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel. This will reveal itself in the fact that the probability of the selection of certain nodes is increased. By using this information it becomes possible, to an extent, to detect malicious tunnels.
